---
title: "HW1"
author: "Minh Luc, Devin Pham, Kyle Moore"
date: "Friday of Week 1, 04/01/2022"
output: pdf_document
urlcolor: blue
---

This is a template `Rmarkdown` file. Please find your partners and form a group for the assignments and final project. It is better to not change after your group is fixed. 


Please read `Math189_HW_template.Rmd` carefully when you write your reports, and use the template file `Math189_HW_template.Rmd` to generate your reports. If you generate your report as a html file, please save it as a pdf file. Please submit your report to **Gradescope** before the deadline. 

***

# Question 0 
Please write down you name and ID like below: 

### Member 1: 
* Name: Minh Luc
* Student ID: A17209607

### Member 2: 

* Name: Kyle Moore
* Student ID: A14271413

### Member 3: 

* Name: Devin Pham
* Student ID: A17198936

***

# Question 1. 

*Let $Z \sim N(0,1)$.

(a) *$P(Z > 1)$*; 

	**Answer:**
	The probability can be calculated by 
	```{r}
	p <- pnorm(q = 1,mean = 0,sd = 1,lower = FALSE)
	print(p)
	p3 <- round(p, digits = 3) # x rounded to 3 decimal places    
	print(p3)
	```
	Therefore, 
	$$
		P(Z > 1) \approx 0.159. 
	$$ 

(b) *$P(Z < -1.06)$;* 

	**Answer:**
	The probability can be calculated by 
	```{r}
	p <- pnorm(q = -1.06,mean = 0,sd = 1,lower = TRUE)
	print(p)
	p3 <- round(p, digits = 3) # x rounded to 3 decimal places    
	print(p3)
	```
	Therefore, 
	$$
		P(Z < -1.06) \approx 0.145. 
	$$ 

(c) *$P(-2.33 < Z \leq 1.06)$.*

	**Answer:**
	The probability can be calculated by 
	```{r}
	p <- pnorm(q = 1.06,mean = 0,sd = 1,lower = TRUE) - pnorm(q = -2.33,mean = 0,sd = 1,lower = TRUE)
	print(p)
	p3 <- round(p, digits = 3) # x rounded to 3 decimal places    
	print(p3)
	```
	Therefore, 
	$$
		P(-2.33 < Z \leq 1.06) \approx 0.846.
	$$ 

*** 


# Question 2. 

*Let $(X,Y)$ be a random vector whose pdf is given by* 
$$
	f_{X,Y}(x,y) = \frac{2}{3}(x  + 2y), \quad 0 \leq x \leq 1,  0 \leq y \leq 1. 
$$

(a) *Find the marginal distribution of $X$.* 

	**Answer:**
	The marginal distribution of $X$ is given by 
	$$
	\begin{aligned}
		f_{X}(x) & =  \int_0^1 f_{X, Y} (x, y) dy \\
				 & = \int_0^1 \biggl( \frac{2}{3}(x + 2y) \biggr) dy \\
				 & = \frac{2}{3} x \int_0^1 dy + \frac{2}{3} \int_0^1 2y dy \\
				 & = \frac{2}{3} x \times 1 + \frac{2}{3} \times y^2 \Big\vert_0^1 \\
				 & = \frac{2}{3} x + \frac{2}{3}, \quad 0 \leq x \leq 1. 
	\end{aligned}
	$$
	Like this, if you want to split a long equation into several lines, you can use `\begin{aligned} ... \end{aligned}` environment or `\begin{split} ... \end{split}` environment inside the `$$ ... $$` environment. Please note that blank lines are not allowed in the `$$ ... $$` environment, otherwise the compile will not be successful. The double backslash `\\` at the end of each line works as a newline character. Use the ampersand character &, to set the points where the equations are vertically aligned. 
	 
(b) *Find the marginal distribution of $Y$.* 

    **Answer:**
	The marginal distribution of $y$ is given by 
	$$
	\begin{aligned}
		f_{Y}(y) & =  \int_0^1 f_{X, Y} (x, y) dx \\
				 & = \int_0^1 \biggl( \frac{2}{3}(x + 2y) \biggr) dx \\
				 & = \frac{2}{3} \int_0^1 xdx + \frac{4}{3} y \int_0^1 dx \\
				 & = \frac{2}{3} \times \frac{x^2}{2} \Bigg\vert_0^1 + \frac{4}{3} y \times 1  \\
				 & = \frac{2}{3} \times \frac{1}{3} + \frac{4}{3} y \\
				 & = \frac{1}{3} + \frac{4}{3} y, \quad 0 \leq y \leq 1. 
	\end{aligned}
	$$
	
(c) *Find $E(X)$, $E(Y)$, $\mathrm{Var}(X)$ and $\mathrm{Var}(Y)$*. 
  
    **$E(X)$:**
    
    Since $E(X) = \int xf_{X}(x)dx$, using the above marginal distribution:
    
    ```{r}
    fx = function(x){
      x*((2/3)*x +(2/3)) # x times marginal fx
    }

    mean_x = integrate(fx, lower=0, upper=1)
    print(round(mean_x$value, digits=3))
    ```
  	$$
		  E(X) \approx .556
	  $$ 
	
    **$\mathrm{Var}(X)$:**
    
    Since $\mathrm{Var}(X) = E(X^2) - E(X)^2$, using the above marginal distribution and $E(X)$:
    
    ```{r}
    fx = function(x){
      x*((2/3)*x +(2/3)) # x times marginal fx
    }
    
    fx2 = function(x){
      (x^2)*((2/3)*x +(2/3)) # x^2 times marginal fx
    }

    var_x = (integrate(fx2, lower=0, upper=1)$value - 
               (integrate(fx, lower=0, upper=1)$value)^2)
    print(round(var_x, digits=3))
    ```
    $$
      \mathrm{Var}(X) \approx .080
    $$
    
    **$E(Y)$:**
    
    Since $E(Y) = \int yf_{Y}(y)dy$, using the above marginal distribution:
    
    ```{r}
    fy = function(y){
      y*((1/3) +(4/3)*y) # y times marginal fy
    }

    mean_y = integrate(fy, lower=0, upper=1)
    print(round(mean_y$value, digits=3))
    ```
  	$$
		  E(Y) \approx .611
	  $$ 
    
    **$\mathrm{Var}(Y)$:**
    
    Since $\mathrm{Var}(Y) = E(Y^2) - E(Y)^2$, using the above marginal distribution and $E(Y)$:
    
    ```{r}
    fy = function(y){
      y*((1/3) +(4/3)*y) # y times marginal fy
    }
    
    fy2 = function(y){
      (y^2)*(((1/3) +(4/3)*y)) # y^2 times marginal fy
    }

    var_y = (integrate(fy2, lower=0, upper=1)$value - 
               (integrate(fy, lower=0, upper=1)$value)^2)
    print(round(var_y, digits=3))
    ```
    $$
      \mathrm{Var}(Y) \approx .071
    $$
    
(d) *Find $\mathrm{Cov}(X, Y)$*. 

      We will use the equation $\mathrm{Cov}(X, Y) = E(XY) -E(X)E(Y) \\$
	 
	$$
	\begin{aligned}
		E(XY) & =  \int_0^1 \int_0^1 xy f_{X, Y} (x, y) dxdy \\
				 & = \int_0^1 \int_0^1 xy \biggl( \frac{2}{3}x + \frac{4}{3}y \biggr) dxdy \\
				 & = \frac{1}{3} \int_0^1 \int_0^1 \biggl( 2x^2y + 4xy^2 \biggr) dxdy \\
				 & = \frac{1}{3} \int_0^1 2y \frac{x^3}{3} \Bigg\vert_0^1 + 4y^2 \frac{x^2}{2} \Bigg \vert_0^1 dy\\
				 & = \frac{1}{3} \int_0^1 2y^2 + \frac{2}{3} y dy\\
				 & = \frac{1}{3} \Bigg(\frac{2}{3} \frac{y^2}{2} \Bigg \vert_0^1 + 2 \frac{y^3}{3} \Bigg \vert_0^1 \Bigg)\\
				 & = \frac{1}{3} \bigg(\frac{1}{3} + \frac{2}{3} \bigg) \\
				 & = \frac{1}{3} \approx .333
	\end{aligned}
	$$
      Then plug into the equation:

	$$
	\begin{aligned}
		\mathrm{Cov}(X, Y) & = E(XY) -E(X)E(Y) \\
				 & = .333 - (.556)(.611) \\
				 & = .333 -  .339716 \\
				 & = .006716 \approx .007
	\end{aligned}
	$$

(e) *Find $\mathrm{Cor}(X, Y)$*. 
 
	$$
	\begin{aligned}
		\mathrm{Cor}(X, Y) & = \frac{\mathrm{Cov}(X, Y)}{\sigma_{X} \sigma_{Y}} \\
				 & =  \frac{.007}{\sqrt{Var(X)} \sqrt{Var(Y)}} \\
				 & = \frac{.007}{\sqrt{.080} \sqrt{.071}} \\
				 & = .0928804 \approx .093
	\end{aligned}
	$$
***

# Question 3. 

(a) *Let $n \geq 1$ and let $X_1, \dots, X_n$ be a sample from $N(\mu, \sigma^2)$, where $\mu$ and $\sigma^2$ are both unknown.  Provide an estimator $\hat{\mu}$ of the unknown parameter $\mu$?*

	
	**Answer:**
	An estimator of the population mean is given by 
$$
	\hat{\mu} = \bar{X} = \frac{1}{n} \sum_{i = 1}^n X_i = \frac{1}{n} (X_1 + \dots + X_n).
$$
	 

(b) *Following (a), provide an estimator $\hat{\sigma}^2$ of the unknown parameter $\sigma^2$*.

    *Let* $n \geq 1$ and let $X_1, \dots, X_n$ be a sample from $N(\mu, \sigma^2)$, where $\mu$ and $\sigma^2$ are both unknown.\linebreak 
    **Answer:** An estimator of the population variance is given by
    
  $$
    \hat{\sigma}^2 = {s^2} = \frac{\sum_{i = 1}^n (X_i - \bar{X})^2}{n-1}
  $$

(c) *Read the 
[`R` documentation webpage](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/Normal) again, and use `rnorm` to generate `n = 10` normal random numbers with `mean = 1` and `sd = 3`*. 

	```{r}
	rnorm(n = 10, mean = 1, sd = 3)
	```
	
	However, when we re-run the line above, the result is different: 

	```{r}
	rnorm(n = 10, mean = 1, sd = 3)
	```
	
	To keep the results unchanged, we can set a random seed every time before we use the `rnorm` function: 
	```{r} 
	set.seed(1)
	rnorm(n = 10, mean = 1, sd = 3)
	set.seed(1)
	rnorm(n = 10, mean = 1, sd = 3)
	```

	*Now, choose an arbitrary integer as your own seed, and generate `n = 5` normal random numbers with `mean = 2` and `sd = 1`.
	Based on (a), find your value of $\hat{\mu}$ using your random numbers and find the difference between $\hat{\mu}$ and the true mean $\mu$*. 
	
    **Answer:**
    ```{r}
    mu <- 2
    set.seed(2)
    rnorm(n = 5, mean = mu, sd = 1)
    set.seed(2)
    muHat <- mean(rnorm(n = 5, mean = mu, sd = 1))
    diff <- muHat - mu
    print(muHat)
    print(diff)
    ```

    Value of $$\hat{\mu} - \mu \approx -0.067$$

(d) *Discuss how can you estimate $\mu$ more accurately, and explain your idea*. 

    We can set n to a higher value and/or set sd to a smaller value. The higher the value of n, the closer we will get to $\mu$,     which is stated by the Law of Large Numbers. Setting the sd to a smaller value will reduce the spread of values from $\mu$.     Without altering the distribution itself, we could minimize the MSE by setting $a$ to the sample mean in the mean squared 
    error fucntion $MSE(a) = \frac{1}{n-1} \sum_{i = 1}^n (x_i - a)^2$
