---
title: "HW4"
author: "Minh Luc, Devin Pham, Kyle Moore"
date: "Friday of Week 4, 04/22/2022"
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
### We all contributed equally for this homework.

# Question 0 

### Member 1: 
* Name: Minh Luc
* Student ID: A17209607

### Member 2: 

* Name: Kyle Moore
* Student ID: A14271413

### Member 3: 

* Name: Devin Pham
* Student ID: A17198936

***

```{r warning=FALSE}
# install the packages if needed by using
# install.packages("...")
library(tidyr)
library(readr)
library(tidytuesdayR)
urlRemote <- 'https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/'
pathGithub <- 'data/2020/2020-07-28/'
fileName <- 'penguins.csv'
penguins <- paste0(urlRemote, pathGithub, fileName) %>% read.csv(header = TRUE)
dfr <- drop_na(as.data.frame(penguins))
head(dfr)
```

***

# Question 1

* **(a)**

    ```{r}
    qf(.95, df1=3, df2=6, lower.tail = FALSE)
    ```
    
* **(b)**

    ```{r}
    p <- 4
    n <- 15
    T2 <- 10
    pf(((n - p) / ((n-1) * p)) * T2, df1=p, df2=n-p, lower.tail = FALSE)
    ```

***

# Question 2

* **(a)**
    
  Null hypothesis: $H_0 : \mu = \mu_0$, or $\mu = (44, 17, 100, 4107)$
  
  Alternative hypothesis: $H_1 : \mu \neq \mu_0$, or $\mu \neq (44, 17, 100, 4107)$

* **(b)**

    ```{r}
    library(DescTools)
    
    X <- dfr[1:50, 3:6]
    mu <- colMeans(X)
    mu0 <- c(44, 17, 200, 4207)
    
    print(mu)     # print sample mean vector
    
    n <- nrow(X)  # num data points
    p <- ncol(X)  # num variables
    S <- cov(X)   # sample covariance matrix
    
    (Tsquare = n * t(mu-mu0) %*% solve(S) %*% (mu-mu0)) # not scaled T^2 stat

    HotellingsT2Test(x=X,mu=mu0, test="f")  # scaled T^2 stat
    ```

* **(c)**

  We have $n = 50, p = 4$, therefore:
  
  $$
      \frac{(n - 1)p}{n - p} F_{p, n-p} = \frac{(50 - 1)4}{50 - 4} F_{4, 46} = 4.261F_{4, 46}
  $$
  $$
      T^2 \sim 4.261F_{4, 46}
  $$

* **(d)**

  We found the p-value of 2.2e-16 using the Hotelling's one sample $T^2$ test above. This p-value$\approx 0$, and given a significance level of 0.05 and our high $T^2$ statistic, we can reject $H_0$.

* **(e)**

    ```{r}
    
    alpha <- .1
    
    F.quantile <- qf(alpha, p, n-p, lower.tail = FALSE)
    print(F.quantile)
    
    critical_value <- (n-1)*p/(n-p)*F.quantile
    print(critical_value)
    
    
    ```
    
    We reject when $T^2 > 8.8253$

* **(f)**
    
  The 90% confidence ellipsoid for $\mu$ is:
    
  $$
    \begin{aligned}
      R(X) & = \bigg\{ \mu: T^2(\mu) \leq \frac{(n-1)p}{(n-p)F_{p,n-p}(\alpha)}  \bigg\} \\
          & = \bigg\{ \mu: n(\bar{\boldsymbol X} - \mu)^T \boldsymbol S^{-1}(\bar{\boldsymbol X} - \mu) \leq \frac{(49)4}{(46)F_{4,46}(.1)}  \bigg\} \\
          & = \bigg\{ \mu: 50(\bar{\boldsymbol X} - \mu)^T \boldsymbol S^{-1}(\bar{\boldsymbol X} - \mu) \leq 8.8253  \bigg\} \\
    \end{aligned}
  $$
  Where
  $$
      \bar{\boldsymbol X} =
      \begin{bmatrix}
        38.916 & 18.774 & 187.140 & 3706.500
      \end{bmatrix}
  $$
  $$
    \boldsymbol S =
    \begin{bmatrix}
      6.2728000 & 0.9271592 & 2.9160816 & 451.2714286 \\
      0.9271592 & 1.3868612 & 3.7057551 & 310.1724490 \\
      2.916082 & 3.705755 & 41.796327 & 1234.785714 \\
      451.2714 & 310.1724 & 1234.7857 & 202010.4592 \\
    \end{bmatrix}
  $$
  

* **(g)**

  The confidence intervals (CI) for each component are
  
  $$
    \begin{aligned}
      \mu_j & \in \bar{\boldsymbol x}_j \pm \sqrt{\frac{(n-1)p}{(n-p)}F_{p,n-p}(\alpha)} \times \frac{s_j}{\sqrt{n}}, j = 1,...,p\\
      \mu_1 & \in 38.916 \pm \sqrt{\frac{(49)4}{(46)}F_{4,46}(0.1)} \times \frac{\sqrt{6.278}}{\sqrt{50}} \\
       & \in 38.916 \pm 8.8253 \times 0.354 \\
       & \in 38.916 \pm 3.127 \\
       & \in [35.789, 42.043] \\
      \mu_2 & \in 18.774 \pm \sqrt{\frac{(49)4}{(46)}F_{4,46}(0.1)} \times \frac{\sqrt{1.387}}{\sqrt{50}} \\
       & \in 18.774 \pm 8.8253 \times 0.167 \\
       & \in 18.774 \pm 1.470 \\
       & \in [17.304, 20.244] \\
      \mu_3 & \in 187.14 \pm \sqrt{\frac{(49)4}{(46)}F_{4,46}(0.1)} \times \frac{\sqrt{41.796}}{\sqrt{50}} \\
       & \in 187.14 \pm 8.8253 \times 0.914 \\
       & \in 187.14 \pm 8.066 \\
       & \in [179.074, 195.206] \\
      \mu_4 & \in 3706.5 \pm \sqrt{\frac{(49)4}{(46)}F_{4,46}(0.1)} \times \frac{\sqrt{202010.459}}{\sqrt{50}} \\
       & \in 3706.5 \pm 8.8253 \times 63.563 \\
       & \in 3706.5 \pm 560.959 \\
       & \in [3145.541, 4267.459] \\
    \end{aligned}
  $$

* **(h)**

    ```{r}
      bonferroni_t <- qt((.1/(2*4)), df=49, lower.tail = FALSE)
      bonferroni_t

      for (x in 1:4) {
        print(x)  # which mu iteration it is on
        print(mu[x])  # value of current mu
        print(S[x,x]) # variance of current mu
        print("left interval")
        print(mu[x] - bonferroni_t * sqrt(S[x,x]/n))  # find right interval
        print("right interval")
        print(mu[x] + bonferroni_t * sqrt(S[x,x]/n))  # find left interval
      }
    ```

  $$
    \begin{aligned}
      \mu_1 & \in [38.097, 39.735] \\
      \mu_2 & \in [18.389, 19.159] \\
      \mu_3 & \in [185.026, 189.254] \\
      \mu_4 & \in [3559.519, 3853.481] \\
    \end{aligned}
  $$