---
title: "HW6"
author: "Minh Luc, Devin Pham, Kyle Moore"
date: "Friday of Week 6, 05/06/2022"
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
### We all contributed equally for this homework.

# Question 0 

### Member 1: 
* Name: Minh Luc
* Student ID: A17209607

### Member 2: 

* Name: Kyle Moore
* Student ID: A14271413

### Member 3: 

* Name: Devin Pham
* Student ID: A17198936

***

\newpage

# Question 1
    
* **(a)**
    ```{r}
    library(ISLR2)
    
    lm.fit = lm(mpg ~ acceleration, data=Auto)
    1
    summary(lm.fit)
    ```
    
  **Answer:**
  
  $\hat{\beta_1} = 1.1976$ and our estimated standard error of $\hat{\beta_1} = .1298$.

* **(b)**

  **Answer:**
  
  Our test statistic is $t = \frac{\hat{\beta_1} - 0}{\widehat{\mathrm{SE}}(\hat{\beta_1})} = \frac{1.1976}{.1298} = 9.228$ which is confirmed in our summary output for the linear model, and our p-value $=2.2\mathrm{e}{-16}$. Therefore we can reject our null hypothesis that $H_0 : \hat\beta_1 = 0$.

* **(c)**

  **Answer:**
  
  Our residual standard error from the summart $= 7.08 = \hat\sigma$ and therefore $\hat\sigma^2 = 7.08^2 = 50.1264$.
  
* **(d)**
    ```{r}
    confint(lm.fit)
    ```
    
  **Answer:**
  
  Our 95% confidence interval is (.9424566, 1.452792).
  
***
  
# Question 2
    
* **(a)**

    ```{r}
    lm.fit = lm(mpg ~ cylinders + displacement + horsepower + weight + 
                  acceleration + year + origin, data=Auto)
    
    summary(lm.fit)
    ```
  
  **Answer:**
  
  This model has 7 predictors and they are cylinders, displacement, horsepower, weight, acceleration, year, and origin.
  
* **(b)**

  **Answer:**
  
  Using the summary above our coefficients are:
  $$
  \begin{aligned}
  \text{Cylinders: }
    \hat\beta_1 &= -0.493376 \\
  \text{Displacement: }
    \hat\beta_2 &= 0.019896 \\
  \text{Horsepower: }
    \hat\beta_3 &= -0.016951 \\
  \text{Weight: }
    \hat\beta_4 &= -0.006474 \\
  \text{Acceleration: }
    \hat\beta_5 &= 0.080576 \\
  \text{Year: }
    \hat\beta_6 &= 0.750773 \\
  \text{Origin: }
    \hat\beta_7 &= 1.426141 \\
  \end{aligned}
  $$
  
* **(c)**

  **Answer:**
  
  Using the summary above our p-values are:
  $$
  \begin{aligned}
  \text{Cylinders, }
    \hat\beta_1: p-value &= 0.12780 \\
  \text{Displacement, }
    \hat\beta_2: p-value &= 0.00844 (**) \\
  \text{Horsepower, }
    \hat\beta_3: p-value &= 0.21963 \\
  \text{Weight, }
    \hat\beta_4: p-value &= < 2e-16 (***) \\
  \text{Acceleration, }
    \hat\beta_5: p-value &= 0.41548 \\
  \text{Year, }
    \hat\beta_6: p-value &= < 2e-16 (***) \\
  \text{Origin, }
    \hat\beta_7: p-value &= 4.67e-07 (***) \\
  \end{aligned}
  $$
  
  The variables that are helpful in predicting mpg are displacement$(\hat\beta_2 \text{ coefficient})$, weight$(\hat\beta_4 \text{ coefficient})$, year$(\hat\beta_6 \text{ coefficient})$, and origin$(\hat\beta_7 \text{ coefficient})$.
  
* **(d)**

  **Answer:**
  
  Using the summary above, our F-statistic $= 252.4$,
  
  degrees of freedom of 7 and 384, 
  
  and $p-value:\space < 2.2\mathrm{e-16} \approx 0$.
  
* **(e)**
    ```{r}
    lm.fit = lm(mpg ~ cylinders + horsepower + acceleration, data=Auto)
    
    summary(lm.fit)
    ```
  **Answer:**
  
  Using the summary above our F-statistic $= 262.5$,
  
  degrees of freedom of 3 and 388, 
  
  and $p-value:\space < 2.2\mathrm{e-16} \approx 0$.
  
  Our p-value is very small so we can reject $H_0: \beta_1 = \beta_2 = \beta_3 = 0$. Among all of these predictors, there is at least one predictor that is helpful in predicting mpg.
  
***