---
title: "HW2"
author: "Minh Luc, Devin Pham, Kyle Moore"
date: "Friday of Week 2, 04/08/2022"
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
### We all contributed equally for this homework.

# Question 0 

### Member 1: 
* Name: Minh Luc
* Student ID: A17209607

### Member 2: 

* Name: Kyle Moore
* Student ID: A14271413

### Member 3: 

* Name: Devin Pham
* Student ID: A17198936

***

# Question 1

* **(a)**

    ```{r warning=FALSE}
    # install the packages if needed by using
    # install.packages("...")
    library(tidyr)
    library(readr)
    library(tidytuesdayR)
    urlRemote <- 'https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/'
    pathGithub <- 'data/2020/2020-07-28/'
    fileName <- 'penguins.csv'
    penguins <- paste0(urlRemote, pathGithub, fileName) %>% read.csv(header = TRUE)
    dfr <- drop_na(as.data.frame(penguins))
    head(dfr)
    ```

* **(b)**

    ```{r warning=FALSE}
    nrow(dfr) # number of rows
    ncol(dfr) # number of columns
    ```
  
  There are `r nrow(dfr)` rows and `r ncol(dfr)` columns in the dataframe(dfr).

***

# Question 2

* **Find the mean vector, covariance matrix and correlation matrix of X:**

    ```{r}
    X <- dfr[,3:6] # assign all rows, but only columns 3-6 to X

    colMeans(X) # mean vector containing the means for each column in X
    
    cov(X) # compute the covariance matrix of X
    
    cor(X) # compute the correlation matrix of X
    ```

* The variance-covariance matrix is a symmetric matrix that represents how the variables are correlated: positively correlated, negatively correlated, or uncorrelated. The diagonal         represents the variance of each variable itself. It is symmetric due to the fact that $\mathrm{Cov}(X,Y) = \mathrm{Cov}(Y,X)$.

* The correlation matrix is a standardized version of the variance-covariance matrix that represents the strength of the correlation between two variables where $-1 \leq correlation        \leq 1$. Entries closer to 1 are more strongly positively correlated, those closer to -1 are strongly negatively correlated, and those near 0 are weakly or uncorrelated. The diagonals     are all 1's because each variable is completely correlated with itself.

***

# Question 3

* **(a)**:

* **(b)**:

* **(c)**:

* **(d)**:

***

# Question 4



***

# Question 5

* **(a)**:

* **(b)**:

* **(c)**:

* **(d)**:

***